Granular measures of agricultural land-use influence lake nitrogen and phosphorus differently at macroscales

### 2020-04-17 manuscript/manuscript.Rmd
center equation

As a more granular representation of watershed agricultural land use, we measured the proportion of land cover in agricultural and “natural” land-uses in 100-m buffers of lake shorelines and streams for each lake watershed. We chose a 100-m buffer width because this width is inclusive of nearly all “riparian buffers” (Mayer et al. 2007). Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes. We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface e (Stachelek 2019) to the National Hydrography Network (USGS 2019). We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, USDA 2019) where we used the python package gssurgo (Stachelek 2019) to access gSSURGO  products. One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody (USDA 2019). Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by Ruddy et al. (2006). We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE (Soranno and Cheruvelil 2017) using the area-weighted interpolation functions provided by the sf R package (Pebesma 2019). All of our data and data processing code are available at [Zenodo DOI].

@@

\begin{equation}
\begin{split}
& y_i = N(\alpha_{j(i)} + \beta_1 * X_{1i}...\beta_n * X_{ni} + \gamma_{1j(i)} * W_{1i} + \gamma_{mj{i}} * W_{mi})\\
& \binom{\alpha_j}{\gamma_{1j}} \sim MVN\left( \binom{\mu_\alpha}{\mu_{\gamma1}}, \Sigma \right)
\label{eqn1} 
\end{split}
\end{equation}

>>>>

As a more granular representation of watershed agricultural land use, we measured the proportion of land cover in agricultural and “natural” land-uses in 100-m buffers of lake shorelines and streams for each lake watershed. We chose a 100-m buffer width because this width is inclusive of nearly all “riparian buffers” (Mayer et al. 2007). Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes. We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface (Stachelek 2019) to the National Hydrography Network (USGS 2019). We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, USDA 2019) where we used the python package gssurgo (Stachelek 2019) to access gSSURGO  products. One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody (USDA 2019). Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by Ruddy et al. (2006). We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE (Soranno and Cheruvelil 2017) using the area-weighted interpolation functions provided by the sf R package (Pebesma 2019). All of our data and data processing code are available at [Zenodo DOI].

@@

\begin{equation}
\begin{aligned}
y_i = N(\alpha_{j(i)} + \beta_1 &* X_{1i}...\beta_n * X_{ni} + \gamma_{1j(i)} * W_{1i} + \gamma_{mj{i}} * W_{mi})\\
& \binom{\alpha_j}{\gamma_{1j}} \sim MVN\left( \binom{\mu_\alpha}{\mu_{\gamma1}}, \Sigma \right)
\label{eqn1} 
\end{aligned}
\end{equation}
